---
title: "Reproducible paper with R"
author:
- Shujie Wang, swang@ldeo.columbia.edu
- 'Patrick '
- Marco
date: "`Sys_Date()`"
output:
  pdf_document: default
  html_document: default
bibliography: references.bib
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install.packages(c("broom","captioner"))

```

```{r}
library(ggplot2)
library(knitr)
library(captioner)
library(broom)
```


```{r, echo=FALSE,message=FALSE, results="hide"}

data("diamonds")
head(diamonds)

```
```{r figcaps, echo=FALSE, message=FALSE, results='hide'}
# Figure and table caption setup
tbl_caps <- captioner(prefix = "Table")
tbl_caps("themodel", "This is a broomed linear model summary table.")
cap_themodel <- tbl_caps("themodel")

fig_caps <- captioner(prefix = "Figure")
fig_caps("pricevscarat", "The relationship between price and carat for the diamonds dataset.")
cap_pricevscarat <- fig_caps("pricevscarat")
```

# Abstract



# Keywords


# 1. Introduction

I really like using R [@RCoreTeam] for science because of tools like RStudio [@RStudio] and RMarkdown [@RMarkdown].
This document is a quick demonstration of writing an academic paper in RMarkdown.
There's a lot of other resources available on the web but hopefully you'll find this document useful as an example.


# 2. Method

We can also put some more advanced math in our paper and it will be beautifully typeset:

\[\sum_{i=1}^{N}{log(i) + \frac{\omega}{x}}\]



# 3. Results
```{r pricevscarat, echo=FALSE, fig.cap=cap_pricevscarat, fig.width=8, fig.height=4, fig.align='center', cache=TRUE}
ggplot(diamonds,aes(x = carat, y =price, color = clarity))+
  geom_point()+
  labs(x="Carats", y="price")

```



```{r}

mod<-lm(price ~ carat, diamonds)
kable(tidy(mod), digits=2, caption=cap_themodel)
```



# 4. Discussion



# Reference

